\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-22 nips2015.tex
fixups + more

\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

@@

\maketitle

\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
imcomplete information and perfect recall (like Texas Hold'em
Poker) based on the notion of enlarged subgradients.
Our algorithm only performs basic iterations (i.e iterations
involving no calls to external first-order oracles, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with imcomplete information
and perfect recall. The number of iterations need to produce a Nash
equilibrium with a given precision is inversely proportion to the
precision. The applicability to the latter kind of games is thanks to
the sequence-form representation \cite{koller1992complexity}. As
proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
\end{abstract}

@@

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0, \text{ if } x \in C;\hspace{.3em} i_c(x) = \infty\text{
    otherwise.}
\end{eqnarray}

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{h\in \mathbb{R}^n | f(z)  \ge f(x) + \langle h, z - x\rangle \forall
z \in X\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. Given $\tau > 0$, the function
\begin{eqnarray}
  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + \tau f(z),
\end{eqnarray}

is called the \textit{proximal operator} of $f$ at rank $\tau$.
The interested reader should refer to
\cite{rockafellar1997convex,combettes2011proximal} for a more
elaborate exposition of convex-analytical concepts and their use in
optimization.

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$,
\item have control over how far we are from the set of equilibria,
\item cope  with infinite primal-dual gaps.
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq.
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

Also, define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
  \begin{equation}
      K :=
      \left[
        \begin{array}{cc}
          A & -E_1^T \\
          E_2 & 0_{l_2, l_1}
        \end{array}
        \right],\hspace{.5em}
    \Psi_1(y, p, x, q)
    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
\end{equation}

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.
\qed

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we derive the algorithm which is the main object of
this manuscript.

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ the set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
- x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

The idea behind $\epsilon$-subgradients is the following: given a
function $f$ which we wish to minimize, replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\exists v \in \partial_\epsilon f(x)$, for some small
perturbation vector $v$''. In fact, it is easy to see that, for each
$x \in X$, $(\partial_\epsilon f(x))_{\epsilon > 0}$ is a decreasing
sequence of sets which converges to $\partial f(x)$.

This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

@@

\subsection{Algorithm and convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  $p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State $\Delta x^{(k+1)} \leftarrow x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow q^{(k+1)}-q^{(k)}$
\State  $q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$
\State $\Delta y^{(k+1)} \leftarrow y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$
\State $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} + \frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
\end{eqnarray}

@@

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
one easily computes the proximal operators $g_1$ and $g_2$ as
\begin{eqnarray*}
  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
  \lambda e_2).
  \end{eqnarray*}

>>>>

\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
%\usepackage{times}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

@@

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker) based on the notion of enlarged
  subgradients. Our algorithm only performs basic iterations (i.e
  iterations involving no calls to external first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles, the size of the
  representation being linear in ... The number of iterations needed
  to produce a Nash equilibrium with a given precision is inversely
  proportional to the desired precision. As proof-of-concept, we apply our
  algorithm to solve Kuhn 3-card Poker.
\end{abstract}

@@

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} the function defined by
\begin{eqnarray}
  \prox_f: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z),
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthongal projectors. One also has the useful
characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

The interested reader should refer to
\cite{combettes2011proximal} for
a more elaborate exposition of proximal operators and their
use in modern convex-optimization.

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$,
\item have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
  \begin{equation}
      K :=
      \left[
        \begin{array}{cc}
          A & -E_1^T \\
          E_2 & 0
        \end{array}
        \right],\hspace{.5em}
    \Psi_1(y, p, x, q)
    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
\end{equation}

@@

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.
\qed

@@

\section{The proposed algorithm}
\label{sec:algo}
\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.
\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}

The idea behind $\epsilon$-subgradients is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

@@

\subsection{Algorithm and convergence rate}
We now derive the algorithm derive the algorithm which is the main object of
this manuscript.

\begin{algorithm}
\label{Tab:algo}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  $p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow
q^{(k+1)}-q^{(k)}$, \hspace{.5em}$q^{(k+1)}
\leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists an index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
\end{eqnarray}

@@

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
one easily computes the proximal operators $g_1$ and $g_2$ as
\begin{eqnarray}
  \prox_{\lambda g_1}(y, p) \equiv ((y)_+, p - \lambda
  e_1),\hspace{.5em} \prox_{\lambda g_2}(x, q) \equiv ((x)_+, q -
  \lambda e_2).
  \end{eqnarray}
